\iffalse
   Copyright 2025 shaun <shaunsbabar2@gmail.com>
   
   This program is free software; you can redistribute it and/or modify
   it under the terms of the GNU General Public License as published by
   the Free Software Foundation; either version 2 of the License, or
   (at your option) any later version.
   
   This program is distributed in the hope that it will be useful,
   but WITHOUT ANY WARRANTY; without even the implied warranty of
   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
   GNU General Public License for more details.
   
   You should have received a copy of the GNU General Public License
   along with this program; if not, write to the Free Software
   Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston,
   MA 02110-1301, USA.
\fi

\documentclass[a4paper,12pt]{exam}  % paper is set to a4 and font size is set to 12pt
\usepackage{mathptmx} % set font family to time-new-roman

\input{mcq-setting.tex}


% The document starts here....
\begin{document}

\begin{flushleft}
Q1. \textbf{Multiple Choice questions}\hspace*{\fill} \textbf{(10 Points)}
\end{flushleft}

% mcq questions start here...
\begin{questions}
\question What is the capital city of Canada?
\choice{Toronto}{Vancouver}{Ottawa}{Montreal}{c}

\question Which planet is known as the Red Planet?
\choice{Jupiter}{Mars}{Venus}{Mercury}{b}

\question Who wrote the play Romeo and Juliet?
\choice{William Shakespeare}{Charles Dickens}{Jane Austen}{Leo Tolstoy}{a}

\question  What is the chemical symbol for gold?
\choice{Ag}{Go}{Gd}{Au}{d}

\question In computing, what does CPU stand for?
\choice{Central Process Unit}{Computer Processing Unit}{Central Processing Unit}{Core Processing Utility}{c}
\end{questions}

\newpage

% comment the line bellow for not to show answers
\showallanswers

\end{document}
